---
title: "Simulation Study for T-ridge"
author: "Shih-Ting Huang"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Settings

##### Simulation parameters : 
1. num.runs : Number of runs of the test (for averaging). 

2. num.obs : Number of observations(n). 

3. num.par : Number of parameters(p). 

4. k : Magnitude of mutual correlations. 

5. Test.case : Test cases for generalized linear models ("gaussian", "poisson", or "binomial"). 

6. Stn : Signal-to-noise ratio for gaussian test case. 

```{r}
num.runs <- 1  
num.obs <- 100 
num.par <- 300 
k <- 0 
Test.case <- "gaussian"
Stn <- 10
```


### Required packages :

1. glmnet : Applying cross validation for generalized linear models.

2. MASS : Creating samples from multivariate normal distribution. 

```{r}
library(glmnet) 
library(MASS) 
```

### Loading additional functions:

```{r}
source("./Additional functions/qnorm.R")
source("./Additional functions/MeanFunction.R")
source("./Additional functions/bFunction.R")
source("./Additional functions/MeanPrime.R")
source("./Additional functions/ObjectiveFunction.R")
source("./Additional functions/Gradient.R")
source("./Additional functions/ObjectEdr.R")

```

```{r include=FALSE}
# TREX parameters
if(Test.case=="gaussian") {
  TREX.c.vector <- 2 
} else {
  TREX.c.vector <- 1
}

class.num <- 1

if(Test.case == "gaussian") {
  stn <- Stn 
} else {
  stn <- NA
}

##### Functions
GradientEdr <- function(theta) {
  if(Test.case=="gaussian") {
    derivative <- t(X) %*% (y - X %*% theta)
    result <- -2 * derivative + u * theta / qnorm(2, theta)
    return(result)
  } else {
    loss <- sum(y * as.vector(X %*% theta) - bFunction(X, theta)) 
    tune.vector <- as.vector(t(y - MeanFunction(X, theta)) %*% X)
    result <- -tune.vector  + u * theta / qnorm(2, theta)
    return(result)
  }
}

ObjectRidge <- function(theta) {
  if(Test.case=="gaussian") {
    loss <- as.vector(y - X %*% theta)
    derivative <- as.vector(t(X) %*% (y - X %*% theta))
    result <- (qnorm(2, loss) ^ 2- qnorm(2, y) ^ 2) + r * qnorm(2, theta) ^ 2
    return(result)
  } else {
    loss <- sum(y * as.vector(X %*% theta) - bFunction(X, theta)) 
    tune.vector <- as.vector(t(y - MeanFunction(X, theta)) %*% X)
    regularization <- qnorm(2, theta) ^ 2
    result <- -loss + r * regularization
    return(result)
  }
}

GradientRidge <- function(theta) {
  if(Test.case=="gaussian") {
    derivative <- t(X) %*% (y - X %*% theta)
    result <- -2 * derivative + r * 2 * qnorm(2, theta)
    return(result)
  } else {
    loss <- sum(y * as.vector(X %*% theta) - bFunction(X, theta)) 
    tune.vector <- as.vector(t(y - MeanFunction(X, theta)) %*% X)
    result <- -tune.vector  + r * 2 * qnorm(2, theta)
    return(result)
  }
}

ObjectLs <- function(theta) {
  if(Test.case=="gaussian") {
    loss <- as.vector(y - X %*% theta)
    derivative <- as.vector(t(X) %*% (y - X %*% theta))
    result <- (qnorm(2, loss) ^ 2- qnorm(2, y) ^ 2) 
    return(result)
  } else {
    loss <- sum(y * as.vector(X %*% theta) - bFunction(X, theta)) 
    tune.vector <- as.vector(t(y - MeanFunction(X, theta)) %*% X)
    regularization <- qnorm(2, theta) ^ 2
    result <- -loss 
    return(result)
  }
}

GradientLs <- function(theta) {
  if(Test.case=="gaussian") {
    derivative <- t(X) %*% (y - X %*% theta)
    result <- -2 * derivative 
    return(result)
  } else {
    loss <- sum(y * as.vector(X %*% theta) - bFunction(X, theta)) 
    tune.vector <- as.vector(t(y - MeanFunction(X, theta)) %*% X)
    result <- -tune.vector
    return(result)
  }
}

# Initialize absolute error
errors.TREX <- matrix(nrow=num.runs, ncol=length(TREX.c.vector))
relative.errors.TREX <- matrix(nrow=num.runs, ncol=length(TREX.c.vector))
errors.CV10 <- rep(NA, num.runs)
relative.errors.CV10 <- rep(NA, num.runs)


beta.error.TREX <- matrix(nrow=num.runs, ncol=length(TREX.c.vector))
relative.beta.error.TREX <- matrix(nrow=num.runs, ncol=length(TREX.c.vector))
beta.error.CV10 <- rep(NA, num.runs)
relative.beta.error.CV10 <- rep(NA, num.runs)

ratio <- rep(NA, num.runs)

##### Loop over the number of runs

for (run in 1:num.runs){
  
  ##### Generate the test setting
  
  cat(sprintf("run %d out of %d runs\n", run, num.runs))
  cat("  -> generate test case... ")
  
  # design matrix
  sigma <- matrix(nrow=num.par, ncol=num.par)
  for(rr in 1:num.par) {
    for(cc in 1:num.par) {
      sigma[rr, cc] <- k ^ abs(rr - cc)
    }
  }
  mu <- rep(0, num.par)
  X <- mvrnorm(n = num.obs, mu=mu, Sigma=sigma)
  
  # Normalize each column of the design matrix
  cat("  -> Normalize each column of the design matrix... ")
  norm <- rep(0, num.par)
  for(i in 1:num.par) {
    nv <- as.vector(X[, i])
    norm[i] <- as.numeric(sqrt(t(nv) %*% nv))
    X[, i] <- nv / norm[i]
  }
  cat("done\n")
  
  # Singular value decomposition of X
  if(num.obs < num.par){
    SVD <- svd(X)
    U <- SVD$u
    V <- SVD$v
  } else {
    SVD <- svd(X, nu = num.obs, nv = num.par)
    U <- SVD$u
    V <- SVD$v
  }
  
  # regression vector
  Projection <- V %*% t(V)
  if(Test.case=="gaussian") {
    beta <- rnorm(num.par, mean = 0, sd = 1) 
    beta <- Projection %*% beta
  } else if(Test.case=="poisson") {
    beta <- rnorm(num.par, mean = 0, sd = 1) 
    beta <- Projection %*% beta
  } else {
    beta <- rnorm(num.par, mean = 0, sd = 1) 
    beta <- Projection %*% beta
  }
  
  # outcome
  y <- rep(NA, num.obs)
  for(i in 1:num.obs) {
    if(Test.case == "gaussian") {
      y[i] <- rnorm(1, mean=as.vector(X %*% beta)[i], sd=sqrt(stn ^ -1 * var(X %*% beta)))
    } else if(Test.case == "poisson") {
      y[i] <- rpois(1, lambda=as.vector(exp(X %*% beta))[i])
    } else {
      y[i] <- rbinom(1, size=class.num, prob=as.vector(exp(X %*% beta) / (1 + exp(X %*% beta)))[i]) 
    }
  }
  cat("done\n")

  # Perform the K-fold cross validation pipeline
  cat("  -> Perform the K-fold cross validation pipeline... ")
  if(num.obs < num.par) {
    cv <- cv.glmnet(X, y, nfolds=10, alpha=0, family=Test.case)
    cv.estimation <- glmnet(X, y, alpha=0, family=Test.case, lambda=cv$lambda.min)
    CV.estimator <- as.vector(coef(cv.estimation))[-1]
  } else {
    cv.estimation <- glmnet(X, y, alpha=0, family=Test.case, lambda=0)
    CV.estimator <- as.vector(coef(cv.estimation))[-1]
  }
  cat("done\n")
  
  # Perform the T-ridge pipeline
  cat("  -> compute T-ridge estimators... ")
  
  init <- optim(par=rep(0, num.par), fn=ObjectLs, gr=GradientLs, 
                method="CG")
  init.vector <- init$par
  GlmTrex.estimators <- matrix(nrow=num.par, ncol=length(TREX.c.vector))
  for(trex.e in 1:length(TREX.c.vector)) {
    TREX.c <- TREX.c.vector[trex.e]
    GlmTrex.estimation <- optim(par=init.vector, fn=ObjectiveFunction, gr=Gradient, method="CG")
    GlmTrex.estimators[, trex.e] <- GlmTrex.estimation$par 
  }
  
  length.tuning <- 1000
  edr.lambda <- qnorm(2, GradientLs(GlmTrex.estimators)) / (2 * qnorm(2, GlmTrex.estimators))
  r.max <- edr.lambda + 0.1
  r.min <- max(0.05, (edr.lambda - 0.1))
  if(r.min == Inf || r.max == Inf ) {
    tuning.parameters <- seq(1e+10, 1e+11, length.out=length.tuning)
  } else {
    tuning.parameters <- seq(r.min, r.max, length.out=length.tuning)
  }
  init <- cv.glmnet(X, y, nfolds=10, alpha=0, family=Test.case)
  init.estimation <- glmnet(X, y, alpha=0, family=Test.case, lambda=init$lambda.min)
  init.vector <- as.vector(coef(init.estimation))[-1]
  Ridge.estimators <- matrix(nrow=num.par, ncol=length.tuning)
  cost <- rep(0, length.tuning)
  for(tune in 1:length.tuning) {
    r <- tuning.parameters[tune]
    if(Test.case=="gaussian") {
      estimation <- glmnet(X, y, alpha=0, family=Test.case, lambda=r)
      Ridge.estimators[, tune] <- as.vector(coef(estimation)[-1])
    } else {
      estimation <- optim(par=init.vector, fn=ObjectRidge, gr=GradientRidge, method="CG")
    Ridge.estimators[, tune] <- estimation$par 
    }
    estimator.r <- as.vector(Ridge.estimators[, tune])
    cost[tune] <- ObjectiveFunction(estimator.r) 
  }
  estimator <- Ridge.estimators[, which.min(cost)]
  cat("done\n")
  
  ##### Compute the prediction errors 
  cat("  -> compute errors... ")
  
  # Prediction error
  for(trex.err in 1:length(TREX.c.vector)) {
    errors.TREX[run, trex.err] <- qnorm(2, abs(X %*% (estimator - beta))) / sqrt(num.obs)
  }
  errors.CV10[run] <- qnorm(2, abs(X %*% (CV.estimator - beta))) / sqrt(num.obs) 
  
  #Relative Prediction error
  relative.errors.TREX[run, ] <- errors.TREX[run, ] / qnorm(2, (X %*% beta)) * sqrt(num.obs)
  relative.errors.CV10[run] <- errors.CV10[run] / qnorm(2, (X %*% beta)) * sqrt(num.obs)
  
  # beta error
  for(trex.b.err in 1:length(TREX.c.vector)) {
    beta.error.TREX[run, trex.b.err] <- qnorm(2, (estimator - beta))
  }
  beta.error.CV10[run] <- qnorm(2, (CV.estimator - beta))
  
  #relative beta error
  relative.beta.error.TREX[run, ] <- beta.error.TREX[run, ] / qnorm(2, beta)
  relative.beta.error.CV10[run] <- beta.error.CV10[run] / qnorm(2, beta)
  
  cat("done\n")
}

##### Output results
output.Data <- matrix(nrow = (length(TREX.c.vector) + 1), ncol = 4)
for(case in 1:length(TREX.c.vector)){
  output.Data[case, ] <- c(mean(errors.TREX[, case]), mean(beta.error.TREX[, case]), mean(relative.errors.TREX[, case]), mean(relative.beta.error.TREX[, case]))
}
output.Data[(case + 1), ] <- c(mean(errors.CV10), mean(beta.error.CV10), mean(relative.errors.CV10), mean(relative.beta.error.CV10))
names <- rep("", length(TREX.c.vector))
for(name in 1:length(TREX.c.vector)) {
  names[name] <- paste0("T-ridge", TREX.c.vector[name])
}
if(num.obs < num.par) {
  rownames(output.Data) <- c(names, "10-fold CV")
} else {
  rownames(output.Data) <- c(names, "MLE")
}

colnames(output.Data)<- c("Xbeta", "Beta", "r.Xbeta", "r.Beta")
cat("Simulation Results : \n")
```

```{r echo=FALSE}
output <- 
  matrix(c(round(output.Data[1, 3], 2),
            round(output.Data[2, 3], 2),
            round(output.Data[1, 4], 2),
            round(output.Data[2, 4], 2)), 
         ncol=4, byrow = TRUE)

library(htmlTable)
library(pander)

if(num.obs < num.par) {
  H <- c("T-ridge", "10-fold CV",
                            "T-ridge", "10-fold CV")
} else {
  H <- c("T-ridge(sd)", "MLE(sd)",
                            "T-ridge(sd)", "MLE(sd)")
}

htmlTable(output,
          header =  H,
          rnames = "Mean relative errors",
          rgroup = paste0("Case : ", Test.case),
          n.rgroup = c(1),
          cgroup = c(pander("$\\frac{||X\\hat{\\beta}_{T-ridge} - X\\beta^{*}||_{2}}{||X\\beta^{*}||_{2}}$"), pander("$\\frac{||\\hat{\\beta}_{T-ridge} - \\beta^{*}||_{2}}{||\\beta^{*}||_{2}}$")),
          n.cgroup = c(2,2), 
          caption=paste0("(n,p,k)=(", num.obs, ",", num.par, ",", k, ")"))
```



