---
title: "Simulation Study for T-ridge"
author: "Shih-Ting Huang"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Settings

##### Simulation parameters : 
1. num.runs : Number of runs of the test (for averaging). 

2. num.obs : Number of observations(n). 

3. num.par : Number of parameters(p). 

4. k : Magnitude of mutual correlations. 

5. Test.case : Test cases for generalized linear models ("gaussian", "poisson", or "binomial"). 

6. Stn : Signal-to-noise ratio for gaussian test case. 

```{r}
num.runs <- 1  
num.obs <- 100 
num.par <- 300 
k <- 0 
Test.case <- "gaussian"
Stn <- 10
```


### Required packages :

1. glmnet : Applying cross validation for generalized linear models.

2. MASS : Creating samples from multivariate normal distribution. 

3. htmlTable : Creating html tables for simulation result.

4. pander : Using specified text elements for output results.

```{r}
library(glmnet) 
library(MASS) 
library(htmlTable)
library(pander)
```

### Loading additional functions:

```{r}
source("./Additional functions/qnorm.R")
source("./Additional functions/MeanFunction.R")
source("./Additional functions/bFunction.R")
source("./Additional functions/MeanPrime.R")
source("./Additional functions/ObjectiveFunction.R")
source("./Additional functions/Gradient.R")
source("./Additional functions/ObjectEdr.R")
source("./Additional functions/GradientEdr.R")
source("./Additional functions/ObjectRidge.R")
source("./Additional functions/GradientRidge.R")
source("./Additional functions/ObjectLs.R")
source("./Additional functions/GradientLs.R")
```

### Simulation process:

##### 1. Initialization process.

```{r}
source("./SimulationProcess/Initialize.R")
```

##### 2. Loop over the number of runs : 

###### 2.1 Data generation.

###### 2.2 K-fold cross validation pipeline.

###### 2.3 T-ridge pipeline.

###### 2.4 Compute errors.

```{r}
for (run in 1:num.runs){
  source("./SimulationProcess/DataGeneration.R")
  source("./SimulationProcess/K-foldCV.R")
  source("./SimulationProcess/TRidge.R")
  source("./SimulationProcess/ComputeErrors.R")
}
```

### Results and Output

##### 1. Results

```{r}
source("./SimulationProcess/ResultsOutput.R")
```

##### 2. Output HTML Table

```{r}
htmlTable(output,
          header =  H,
          rnames = "Mean relative errors",
          rgroup = paste0("Case : ", Test.case),
          n.rgroup = c(1),
          cgroup = c(pander("$\\frac{||X\\hat{\\beta}_{T-ridge} - X\\beta^{*}||_{2}}{||X\\beta^{*}||_{2}}$"), pander("$\\frac{||\\hat{\\beta}_{T-ridge} - \\beta^{*}||_{2}}{||\\beta^{*}||_{2}}$")),
          n.cgroup = c(2,2), 
          caption=paste0("(n,p,k)=(", num.obs, ",", num.par, ",", k, ")"))
```

